Active Learning from Blackbox to Timed Connectors

### 2016-01-11 paper/paper.tex
.

\subsection{Active Learning}

@@

\subsection{An Example of the Reo Package}
As mentioned above, our implementation in \texttt{Golang} is well-prepared not only for academic use
but also for practical concurrent programming.

\begin{lstlisting}
int main(int argc, char ** argv)
{
  printf(``Hello world!n'');
  return 0;
}
\end{lstlisting}

>>>>

\subsection{Active Learning}
Active learning is a special case of semi-supervised machine learning in which a learning algorithm
is able to interactively query the user (or some other information source) to obtain the desired
outputs at new data points.\cite{settles2010active}.

@@

\subsection{An Example of the Reo Package}
As mentioned above, our implementation in \texttt{Golang} is well-prepared not only for academic use
but also for practical concurrent programming. The following code shows how to compose an alternator
connector (see Figure \ref{fig:reoconnector}) in \texttt{Golang}. An intact version of this example can be found in our github repo.

\begin{lstlisting}
  package main

  import . './lib/reo'

  func alternator(A, B, C reo.Port) {
    // definition of ports
    M0 := MakePort()
    // similarly define M1 ... M5

    // definition of channels
    go ReplicatorChannel(A, M0, M1)
    go ReplicatorChannel(B, M2, M3)
    go MergerChannel(M4, M5, M6)

    go SyncdrainChannel(M1, M2)
    go SyncChannel(M0, M4)
    go FifoChannel(M3, M5)
  }
\end{lstlisting}
